On exponential sums arising from the classical doubling method

### 2025-04-08 main.tex
Minors

The proof strategy is to prove the following inductive statements
\begin{enumerate}[(a)]
	\item \label{item:follows-for-non-cuspidal}If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$.
	\item \label{item:follows-for-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$, then it holds for all irreducible cuspidal representations of $H$ with $\dim_{\mathbb{E}} V = n$.
\end{enumerate}
The key input to (\ref{item:follows-for-non-cuspidal}) is the multiplicativity of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor. The key input to (\ref{item:follows-for-cuspidal}) is \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.

@@

Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that for every $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$, the exists some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction to $G$ of $\tilde{\pi}$. It thus suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.

@@

	For the right hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift}, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{(s)}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\sigma}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
		\algebraicGroup{L}^{\Frobenius}}{(s)}$.

>>>>

The proof strategy is to prove the following inductive statements
\begin{enumerate}[(a)]
	\item \label{item:follows-for-non-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all representations of $H'$ where $H'$ corresponds to $\left(\hermitianSpace', \innerproduct{\cdot}{\cdot}\right)$ with $\dim_{\quadraticExtension} V' < n$, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$.
	\item \label{item:follows-for-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$, then it holds for all irreducible cuspidal representations of $H$.
\end{enumerate}
The key input to (\ref{item:follows-for-non-cuspidal}) is the multiplicativity of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor. The key input to (\ref{item:follows-for-cuspidal}) is \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.

@@

Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that for every $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$, there exists some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $G$. It thus suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $H = \GroupExtension{G}$.

@@

	For the right hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift}, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{s}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\sigma}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
		\algebraicGroup{L}^{\Frobenius}}{s}$.
